\bf Estimating the number of clusters using Cross Validation

### 2015-10-09 technometrics.tex
Revised the rotation method for correcting high correlation

In practice, one can check such condition using estimated sample covariance matrix for single cluster case. 
If such condition doesn't met, one solution is rotating the matrix to eliminate the correlation between each dimension then perform Gabriel CV method on the rotated data matrix. Another empirically observed solution is 
to leave most columns for clustering, i.e. increase the dimension of $\Sigma_{YY}$. Such solution is especially 
useful for data containing multiple clusters, where neither estimating sample covariance matrices nor
rotating to eliminate correlation is feasible. Although the theory for such solution is available for special cases,
its general version hasn't been developed.

>>>>

In practice, check such condition is tricky. One need to know the covariance matrix of each cluster to check if the condition holds. However, in order to estimate the covariance matrix we need to know the cluster center of each cluster, which in turn need to know the number of clusters in the data. A possible solution is following
\begin{enumerate}
	\item For parameter $k$ starts at $k=1$ do the following
	\begin{enumerate}[label=(\roman*)]
		\item Estimate $k$ cluster centers by applying $k$-means with parameter $k$
		\item Estimate the covariance matrix $\hat{\Sigma}$ for each cluster 
		\item Check the condition for each $\hat{\Sigma}$
		\item If the the condition doesn't hold, rotate that cluster through 
		rotation matrix $R^T$, where $\hat{\Sigma} = RLR^T$ 
		\item Apply previously proposed Gabriel CV method on the rotated data, get estimated number $k^*$
	\end{enumerate}
	\item If $k^* = k$, stop the algorithm and return $k$; otherwise repeat step $1$ for parameter $k+1$
\end{enumerate}
from which we can see the condition checking step can not be separated from the proposed Gabriel CV method.
Another empirically observed solution is to leave out most columns for clustering, i.e. increase the 
dimension of $\Sigma_{YY}$. Such method is observed reducing the impact of correlation on the performance 
of the proposed method. Although the theory for such solution is available for special cases,
its general version hasn't been developed.
